Large-Scale Content-Based Matching of MIDI and Audio Files

### 2015-03-16 paper.tex
Adding related work paragraph

>>>>

The idea of using DTW distance to match MIDI files to audio recordings is not new.
For example, in \cite{hu2003polyphonic}, MIDI-audio matching is done by finding the minimal DTW distance between all pairs of chromagrams of (synthesized) MIDI and audio files.
Our approach differs in a few key ways: First, instead of using chromagrams (a hand-designed representation), we optimize a common representation for MIDI and audio data.
This makes our system flexible with respect to the underlying feature representation used for each modality.
Second, our datasets are many orders of magnitude larger (hundreds of thousands vs.\ hundreds of files), which necessitates a much more efficient approach.
Specifically, by mapping to a Hamming space we greatly speed up distance matrix calculation and our proposed pruning techniques avoid a full DTW distance computation for the majority of file pairs.
